\bf Faster Neural Machine Translation Inference

### 2018-02-22 fast-beam/fast-beam.tex
fast

Our paper follows most closely on from ~\citet{DBLP:conf/emnlp/Devlin17} which achieved faster NMT inference mainly by novel implementation of an existing model. However, we differ by focusing on GPU implementation, specifically the output layer, and the batching algorithm which was not touched on by the previous work. Our model is based on that of ~\citet{D14-1179} but our work is applicable to other models and applications. % rather than CPUs as pursued by ~\cite{DBLP:conf/emnlp/Devlin17}.

@@

As can be seen, the matrix p is iterated over five times - once to add the bias, three times to calculate the softmax, and once to search for the best class. We fuse the three functions into one kernel, a popular optimization technique~\citep{Guevara2009EnablingTP}, making use of the following observations.

@@

Our proposed top-up batching algorithm encode and decode asynchronously. The encoding step, Algorithm~\ref{algo:Encoding for top-up batching}, is similar to the main loop of the standard algorithm but the results are added to a queue to be consumed by the decoding step later.

>>>>

Our paper follows most closely on from ~\citet{DBLP:conf/emnlp/Devlin17} which achieved faster NMT inference mainly by novel implementation of an existing model. However, we differ by focusing on GPU implementation, specifically the output layer, and the batching algorithm which was not touched on by the previous work. Our model is based on that of ~\citet{D14-1179} and ~\citet{sennrich-haddow-birch:2016:P16-12} but our work is applicable to other models and applications. % rather than CPUs as pursued by ~\cite{DBLP:conf/emnlp/Devlin17}.

@@

As can be seen, the matrix p is iterated over five times - once to add the bias, three times to calculate the softmax, and once to search for the best classes. We propose fusing the three functions into one kernel, a popular optimization technique~\citep{Guevara2009EnablingTP}, making use of the following observations.

@@

Our proposed top-up batching algorithm encode and decode asynchronously. The encoding step, Algorithm~\ref{algo:Encoding for top-up batching}, is similar to the main loop of the standard algorithm but the results are added to a queue to be consumed by the decoding step.
